---
title: "main"
author: "Quek Xiu Cheng"
date: "18 November 2015"
output: 
  html_document:
    toc : true
---

This is a document to highlight the steps involved conducting self organizing map analysis with data from the MRTA Projects.

Data are restricted acces and are not included in the repository 

For more infomration please email : x.quek@garvan.org.au


# Dependencies


```{r}
library(edgeR)
library(pheatmap)
library(cluster)
library(R6)
library(reshape2)
library(plyr)
library(kohonen)
library(ggplot2)
source('src/somHelper.R')

```

# Step 1 - Read data ( FPKM Value )

```{r, echo=FALSE}
fpkm <- read.table('data/rsem_gencode/EMP1_resultsGenesFPKM.txt')

classifications <- read.table('data/classification.tsv')

```

# Step 2 - Working on Snail / on / off model only


```{r}


snail_model_fpkm <- fpkm[classifications$snailModel == 'S']

snail_model_fpkm <- snail_model_fpkm[rowSums(snail_model_fpkm > 1 ) >= ncol(snail_model_fpkm),]
snail_model_fpkm_list <- list()

snail_model_fpkm_list$fpkm <- snail_model_fpkm
snail_model_fpkm_list$fpkm_scaled <- apply(snail_model_fpkm, 2, scale, center = T)
snail_model_fpkm_list$fpkm_scaled  <- as.data.frame(snail_model_fpkm_list$fpkm_scaled,row.names = rownames(snail_model_fpkm))

snail_model_fpkm_list$fpkm_log10 <- log10(snail_model_fpkm + 0.25 )
snail_model_fpkm_list$fpkm_scaled_log10 <- apply(snail_model_fpkm_list$fpkm_log10 , 2, scale, center = T)
snail_model_fpkm_list$fpkm_scaled_log10  <- as.data.frame(snail_model_fpkm_list$fpkm_scaled_log10,row.names = rownames(snail_model_fpkm))



snail_model_fpkm_som_list <- lapply(snail_model_fpkm_list, function(x)
                                { set.seed(7);  
                                  som(data=as.matrix(x), grid = somgrid(8,8, "rectangular"), keep.data =T)
                                }) 
snail_model_fpkm_somObj_list <- lapply(snail_model_fpkm_som_list, function(x){
                                somHelper$new(x)
                        })

```


```{r, fig.width=20, fig.height=20}

fpkm_som_plots <- somPlotHelper$new(snail_model_fpkm_somObj_list)

fpkm_som_plots$plotAllCluster()




```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
